Papers

### 2023-10-09 papers.qmd
add link
add JAP paper
format fix
updates to acceptance

## 2023
D. Yarger and **J. D. Tucker**, "Detecting changepoints in globally-indexed functional time series", *Spatial Statistics*, submitted, 2023. [arxiv preprint]()

@@

D. Francom, **J. D. Tucker**, J. G. Huerta, K. Shuler, and D. Ries, "Elastic Bayesian Model Calibration", *Arxiv*, submitted, 2023. [arxiv preprint](https://arxiv.org/abs/2305.08834)

**J. D. Tucker** and D. Yarger, "Elastic Functional Changepoint Detection of Climate Impacts from Localized Sources", *Envirometrics*, in revision, 2023. [arxiv preprint](https://arxiv.org/abs/2211.12687)

>>>>

## 2023
J. Brown, J. P. Davis, **J. D. Tucker**, J. G. Huerta, and K. Shuler, "Quantifying uncertainty in analysis of shockless dynamic compression experiments on platinum, Part 2: Bayesian model calibration", *Journal of Applied Physics*, submitted 2023.

D. Yarger and **J. D. Tucker**, "Detecting changepoints in globally-indexed functional time series", *Spatial Statistics*, submitted, 2023. [arxiv preprint](https://arxiv.org/abs/2308.05915)

D. Francom, **J. D. Tucker**, J. G. Huerta, K. Shuler, and D. Ries, "Elastic Bayesian Model Calibration", *Arxiv*, in revision, 2023. [arxiv preprint](https://arxiv.org/abs/2305.08834)

@@

**J. D. Tucker** and D. Yarger, "Elastic Functional Changepoint Detection of Climate Impacts from Localized Sources", *Envirometrics*, accepted, 2023. [arxiv preprint](https://arxiv.org/abs/2211.12687)
